CS246: Twitter Purification

### 2014-06-08 Paper.tex
Added Zijun's stuff

TODO: Zijun

@@

TODO: Zijun

@@

TODO: add some subsections here?

@@

@@

TODO: listing any more aspects where it didn't work well

@@

RT @RomarioWay300: Who Else

>>>>

\paragraph{} In the Twitter environment, users may often repeat one character in some words several times to express their emotions or to add emphasis to such words. For example, people may say, \textit{I am soooooooooooo happy!}. In this case, the word \textit{so} is stretched by repeating the character `o' many times. We attempt to recover the originally intended words.
\paragraph{} An important observation in English is that no words contain three of the same consecutive characters. Based on this fact, we designed our squeezing algorithm. For each word, we scan the word and check whether it has three or more of the same adjacent characters. If so, our algorithm will squeeze these characters and only keep one or two characters. For example, the word \textit{goooooooooood} will be squeezed to \textit{good} and \textit{god}. Moreover, if we find multiple such "squeezable" sections in a words, we will squeeze them separately and return all possible squeeze results. For example, if we have a word \textit{bammmmmmmmboooooooo}, the final squeeze result will be \textit{bambo, bamboo, bammbo, bammboo}.

@@

\paragraph{} Edit distance is a method of quantifying how dissimilar two words are to one another by counting the minimum number of operations required to transform one string into the other. Different sets of operations can define different edit distances. In this project, we use the Damerau-Levenshtein distance. The operation for this metric is defined as insertion, deletion, substitution of a single letter, and transposition of two adjacent characters. 
\paragraph{}We use the edit distance to generate the candidate list for each words. We generate the candidate list by maintaining a distance-based candidate list and enlarging the candidate list in a iterative way. For example, we first generate the candidate with edit distance = 1 by applying insertion, deletion, substitution and transposition. We call this set S1. Then for each words in S1, we can generate a new set S2 by applying the same operations on the set S1. In this way, we can obtain a candidate set with fixed distance to the original words. Moreover, in each step, in order to avoid generate too much candidates, we only keep candidates that exist in the dictionary. In this project, we limit the maximum distance = 2 to generate the candidate list.

@@

\paragraph{}After the single word correction process, each word has a potential candidate list with corresponding weights. Bigram correction is used to determine the final choice. This algorithm works as follows:
\paragraph{} Assume we have two adjacent words $w_1$ and $w_2$ and they have corresponding candidate lists $p$ and $q$, respectively. We also assume $p[i]$ is the $i^{\text{th}}$ candidate words in the list $p$ and $q[j]$ is the $j^{\text{th}}$ candidate in $q$. We refer to each candidate pair ($p[i], q[j]$) as a bigram unit. For each bigram unit, we check its frequency in our bigram frequency dictionary. The frequency of the bigram unit is the score of this bigram unit. If the bigram unit is ($p[i],q[j]$), we note this score as $F(p[i],q[j])$. For each candidate, we also have a similarity score to the original words. If we assume the candidate is $p[i]$, the similarity score is noted as $S(p[i])$. For each word, we designate the candidate list of the previous word as $p$, the candidate list of itself as $q$, the candidate list of the word after it as $r$. We use the formula below to calculate the final score of each candidate $q[j]$.
$$R(q[j]) = \max_i(F(p[i],q[j])) \times \max_k(F(q[j],r[k]))\times S(q[j])$$
Finally, among all the $R(q[j])$, we pick the maximum as the final result of $q$.
\paragraph{}For example, suppose we have three candidate lists, $[(a), (good, god), (boy, buy)]$. Assuming the bigram scores are:\\
$
F(a,good)=10\\
F(a, god)=10\\
F(good, boy)=100\\
F(god, boy)=1\\
F(good, buy)=5\\
F(god, buy)=1
$\\
and the similarity score is $S(good)=10, S(god)=3$. So the final scores are:\\
$\begin{array}{lcr}
R(good)&=&F(a,good)\cdot F(good,boy)\cdot S(good)\\
&=&10\cdot100\cdot10 = 10000\end{array}$\\

$\begin{array}{lcr}
R(god)&=&F(a,god)\cdot F(god,buy)\cdot S(god)\\
&=& 10\cdot5\cdot3=150\end{array}$\\
We pick the largest score as our result, finally obtaining \textit{good} as the result for candidates [\textit{good,god}]. 

@@

\\

@@

@@
